Enabling GPU Virtualization in Cloud Environments

### 2015-10-26 paper.tex
revisión 7

\section{\uppercase{Conclusions}}
\label{sec:conclusions}
We have presented a complete study of the possibilities offered by AWS when it comes to GPUs. 
The constraints imposed by this service motivated us to deploy our own private cloud, in order to gain flexibility when working with these accelerators.
For this purpose, we have introduced an extension of OpenStack which easily permits to create GPU-instances and manage the physical GPUs to better profit from them.

As we expected, due to the limited bandwidth of the interconnects used in the experimentation, the performance observed for the GPU virtualized scenarios in the test was quite low.
On the other hand we have created new operation modes that open interesting new ways of using GPUs in situations where the having access to a GPU is more important than having a powerful GPU to boost the performance.

\section{\uppercase{Future work}}
\label{sec:future}
The first in the list of pending work is the upgrade of the interconnection network to one more prone on HPC.
Porting the setup and the tests to an infrastructure with an Infiniband network will shed light on the viability of this kind of solutions for HPC.
The same thought, motivates us to try other Cloud vendors which better support for HPC.

Looking for real situations where performance is less important than flexibility will drive us 
to tools for easily deploying GPU-programming computer labs.

Finally, an interesting future mode is to design new strategies in order to decide where a remote GPUs is created and assigned to a physical device
In particular, innovate scheduling policies can enhance the flexibility given by the GPGPU module for OpenStack.

>>>>

\section{\uppercase{Conclusions}}
\label{sec:conclusions}
We have presented a complete study of the possibilities offered by AWS when it comes to GPUs. 
The constraints imposed by this service motivated us to deploy our own private cloud, in order to gain flexibility when dealing with these accelerators.
For this purpose, we have introduced an extension of OpenStack which can be easily exploited to create GPU-instances as well as manage the physical GPUs to better profit from them.

As we expected, due to the limited bandwidth of the interconnects used in the experimentation, the performances observed for the GPU virtualized scenarios in the tests were quite low.
On the other hand, we have created new operation modes that open interesting new ways to leverage GPUs in situations where having access to a GPU is more important than having a powerful GPU to boost the performance.

\section{\uppercase{Future work}}
\label{sec:future}
The first item in the list of pending work is an upgrade of the network to an interconnect that is more prone to HPC.
In particular, porting the setup and the tests to an infrastructure with an Infiniband network will shed light on the viability of this kind of solutions for HPC.
Similar reasons, motivate us to try other Cloud vendors which better support for HPC.

Looking for real situations where performance is less important than flexibility will drive us to explore alternative tools to easily deploy GPU-programming computer labs.

Finally, an interesting future work is to design new strategies in order to decide where a remote GPUs is created and assigned to a physical device
Concretely, to innovate scheduling policies can enhance the flexibility offered by the GPGPU module for OpenStack.
